---
title: "Misc"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2

---


## Favourite papers

I believe that sharing favourite papers including those outside your projects helps communicate your broad interests.
Here I list a subset of papers which influenced the way I think.


### <u>Population genetics</u>

```{r, echo=F}
library("htmltools")
includeHTML("bib/popgen_html_body.txt")
```

### <u>Behaviour and brain</u>

```{r, echo=F}
library("htmltools")
includeHTML("bib/neuro_behav_html_body.txt")
```

### <u>Complex traits</u>

```{r, echo=F}
library("htmltools")
includeHTML("bib/gen_pheno_html_body.txt")
```

### <u>Phenotypic plasticity, cryptic variation, and evolutionary novelty</u>

```{r, echo=F}
library("htmltools")
includeHTML("bib/evolvability_html_body.txt")
```



## Favourite books

[bookmeter](https://bookmeter.com/users/336463/bookcases/11926459)






## Favourite music





<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/5y0B5zgMwAB0TUGKKoHpKH?utm_source=generator" width="30%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy"></iframe>

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/2TtI5iTMXqW88tzYL4rpUm?utm_source=generator" width="30%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy"></iframe>

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/2uH0rRRWZsHC1DR6MlI5BS?utm_source=generator" width="30%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy"></iframe>

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/album/4ATsr7uNKgh21HOtXHArcN?utm_source=generator" width="30%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy"></iframe>

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/0IHwXjezdnK2hg3yB65WWV?utm_source=generator" width="30%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy"></iframe>

<iframe style="border-radius:12px" src="https://open.spotify.com/embed/playlist/2dEaYRAxiWnjDMjsVOK2re?utm_source=generator" width="30%" height="152" frameBorder="0" allowfullscreen="" allow="autoplay; clipboard-write; encrypted-media; fullscreen; picture-in-picture" loading="lazy"></iframe>





## Podcast (in Japanese)



A friend of mine and I host [a small podcast](https://stopcodonfm.github.io/stopcodon.fm/). 
We introduce papers to each other in a journal club style.
